Endogenous Politics and \\ the Design of Trade Institutions

### 2016-07-22 to-do.tex
turn to-do items into sections

March 30, 2016
\begin{enumerate}
	\item Motivation
		\begin{itemize}
			\item What it's missing: intersection with reality
				\begin{itemize}
					\item Anecdotes
					\item How policy is used
						\begin{itemize}
							\item I thought that escape clause implications \textit{were} this
						\end{itemize}
					\item Something like how GH predicts export taxes but it doesn't work that way in the real world
					\item Well articulated question / paradox
				\end{itemize}
			\item Look at ``Theory of Managed Trade'' model motivation (BS)
			\item Intro doesn't reflect body of paper
			\item What kinds of empirical questions might we ask with this model?
			\item What would be different because we use this model?
			\item Starting from the introduction, I think you make a convincing case that it is important to endogenize the extent of political pressure and I believe this would be THE selling point of the paper. However, you have not completely sold your contribution and its novelty that you bring in the issue of the objective function of the government. Is this aspect crucial for the point you want to make? If yes, it should be integrate with the previous object from the beginning. If not, it should be postponed a bit.
			\item I also find the introduction too long. You could/should split the literature review that begins on page 4 to a separate section. And in any case, I found that you don't engage with the literature in terms of how you contribute/differentiate from it. Again, your main point seems to get lost into the discussion instead of standing out.
			\item You need to think a bit more about the objective(s) of the paper and how best to achieve them.
		\end{itemize}

@@

	\item More on escape clause / WEC

@@

					\item ``Why Are Safeguards under the WTO So Unpopular?'' (World Trade Review 2002), \url{C:\Users\Kristy\Dropbox\Research\PE_shocks\Literature\2016}

@@

	\item Costly state verification

@@

\newpage
	\item BS2005 vs. MRC2007
		\begin{itemize}
			\item Dangerous to build on JLS paper; better to connect to bigger cites or will limit impact, where it can be published
				\begin{itemize}
					\item Perhaps higher level model like BS GE model or some alternative approach that is not so rinky dink (my words)
				\end{itemize}
			\item I like the way you use Bagwell and Staiger (2005) as your benchmark.  But I also wondered whether Maggi and Rodriguez-Clare (2007, henceforth MRC) also offered a useful benchmark.  I know you did have comparisons to their paper in many places but it would be useful if this could be more systematic, and if your paper could draw careful parallels to your assumptions and theirs.  In both papers, the government wants to set a tariff cap in order to be able to extract rents from lobbies afterwards.  But your mechanisms seem quite different.  They have capital mobility whereas your factors are specific to each sector.  If capital is highly immobile they have a hold-up problem, which creates an incentive for lobbies to try to prevent too much liberalization under the agreement.  What drives this feature in your model?  Here I think it would be useful to explain carefully the sequence of events in your set-up more carefully.  What is the relationship between lobby effort level and tariff policy?  Is effort fixed first, after which the government sets its tariff?  If so it seems to me that would drive a kind of hold-up because lobbying effort is sunk.  It would be useful to be clearer about this so we can really understand where the results are coming from and how they compare to MRC.  Having done that, you could bring in ex-ante lobbying and treat it the same way. 
			\item In general it seems to me that you seem to "dependent" on Bagwell and Staiger... (e.g. beginning of Sections 4 and 6).
		\end{itemize}
	\item Structured differently from most papers
		\begin{itemize}
			\item How did Devashish structure his AER paper: the argument, the model?
				\begin{itemize}
					\item This paper is structured differently than the norm---is there a good reason to do it?
					\item Don't want to challenge what people are used to unless I really need to
					\item In general, how do AER papers \textit{look}?
				\end{itemize}
			\item If above I suggest to add a section, I think that the paper is already too long and divided into too many sections but that goes back to my first comment about identifying the key issue/contribution: endogeneity of political pressure and/or objective function. The analysis is also split between strict and weak commitments. Which scenario clearly develops the point/contribution you want to make? Shouldn't the other one occupy a smaller place (i.e. space) of the paper?)
		\end{itemize}
		\item One good idea / do too much
		\begin{itemize}
			\item You can have one good idea in a paper, the rest get lost
			\item At the moment, I find the paper a bit unstructured in that it does a lot but it doesn't sell in a neat and clear way what it is doing.
			\item The paper is already too long and divided into too many sections but that goes back to my first comment about identifying the key issue/contribution: endogeneity of political pressure and/or objective function.
			\item So I'm wondering whether you could dispense with most of the static analysis and get into the repeated game more quickly.
		\end{itemize}
	\item Define $\ga$ before using it
	\item Take out repeats, especially of references to BS2005: In some parts the paper also seem repeating itself: you review Bagwell and Staiger (2005) in Section 2.2 but you provide another summary of the same paper in Section 3. Again, a revised structure may reduce the overlap, make the paper shorter, and be more to the point.
	\item Scrub unnecessary references to weak bindings (since strong are now mostly gone)
	\item Perhaps make a bigger deal of the idea of $\ga$ decreasing function of $\tau$---move out of footnote
\end{enumerate}

>>>>

March 30, 2016

\section{Motivation}
		\begin{itemize}
			\item What it's missing: intersection with reality
				\begin{itemize}
					\item Anecdotes
					\item How policy is used
						\begin{itemize}
							\item I thought that escape clause implications \textit{were} this
						\end{itemize}
					\item Something like how GH predicts export taxes but it doesn't work that way in the real world
					\item Well articulated question / paradox
				\end{itemize}
			\item Look at ``Theory of Managed Trade'' model motivation (BS)
			\item Intro doesn't reflect body of paper
			\item What kinds of empirical questions might we ask with this model?
			\item What would be different because we use this model?
			\item Starting from the introduction, I think you make a convincing case that it is important to endogenize the extent of political pressure and I believe this would be THE selling point of the paper. However, you have not completely sold your contribution and its novelty that you bring in the issue of the objective function of the government. Is this aspect crucial for the point you want to make? If yes, it should be integrate with the previous object from the beginning. If not, it should be postponed a bit.
			\item I also find the introduction too long. You could/should split the literature review that begins on page 4 to a separate section. And in any case, I found that you don't engage with the literature in terms of how you contribute/differentiate from it. Again, your main point seems to get lost into the discussion instead of standing out.
			\item You need to think a bit more about the objective(s) of the paper and how best to achieve them.
		\end{itemize}

@@

\section{More on escape clause / WEC}

@@

					\item ``Why Are Safeguards under the WTO So Unpopular?'' (World Trade Review 2002), %\url{C:\Users\Kristy\Dropbox\Research\PEshocks\Literature\2016}

@@

\section{Costly state verification}

@@

\section{BS2005 vs. MRC2007}
			\item Dangerous to build on JLS paper; better to connect to bigger cites or will limit impact, where it can be published
					\item Perhaps higher level model like BS GE model or some alternative approach that is not so rinky dink (my words)
			\item I like the way you use Bagwell and Staiger (2005) as your benchmark.  But I also wondered whether Maggi and Rodriguez-Clare (2007, henceforth MRC) also offered a useful benchmark.  I know you did have comparisons to their paper in many places but it would be useful if this could be more systematic, and if your paper could draw careful parallels to your assumptions and theirs.  In both papers, the government wants to set a tariff cap in order to be able to extract rents from lobbies afterwards.  But your mechanisms seem quite different.  They have capital mobility whereas your factors are specific to each sector.  If capital is highly immobile they have a hold-up problem, which creates an incentive for lobbies to try to prevent too much liberalization under the agreement.  What drives this feature in your model?  Here I think it would be useful to explain carefully the sequence of events in your set-up more carefully.  What is the relationship between lobby effort level and tariff policy?  Is effort fixed first, after which the government sets its tariff?  If so it seems to me that would drive a kind of hold-up because lobbying effort is sunk.  It would be useful to be clearer about this so we can really understand where the results are coming from and how they compare to MRC.  Having done that, you could bring in ex-ante lobbying and treat it the same way. 
			\item In general it seems to me that you seem to "dependent" on Bagwell and Staiger... (e.g. beginning of Sections 4 and 6).
\section{Structured differently from most papers}
			\item How did Devashish structure his AER paper: the argument, the model?
					\item This paper is structured differently than the norm---is there a good reason to do it?
					\item Don't want to challenge what people are used to unless I really need to
					\item In general, how do AER papers \textit{look}?
			\item If above I suggest to add a section, I think that the paper is already too long and divided into too many sections but that goes back to my first comment about identifying the key issue/contribution: endogeneity of political pressure and/or objective function. The analysis is also split between strict and weak commitments. Which scenario clearly develops the point/contribution you want to make? Shouldn't the other one occupy a smaller place (i.e. space) of the paper?)
\section{One good idea / do too much}
			\item You can have one good idea in a paper, the rest get lost
			\item At the moment, I find the paper a bit unstructured in that it does a lot but it doesn't sell in a neat and clear way what it is doing.
			\item The paper is already too long and divided into too many sections but that goes back to my first comment about identifying the key issue/contribution: endogeneity of political pressure and/or objective function.
			\item So I'm wondering whether you could dispense with most of the static analysis and get into the repeated game more quickly.
\section{Define $\ga$ before using it}
\section{Deal with ``dynamic preferences'' issue}
			\item References from Krishna and Sadowski (2014) ECTA
					\item DILLENBERGER, D., J. S. LLERAS, P. SADOWSKI, AND N. TAKEOKA (2013): ``A Theory of Subjective Learning,'' Working Paper. 
					\item GUL, F., AND W. PESENDORFER (2004): ``Self-Control and the Theory of Consumption,'' Econometrica, 72 (1), 119-158
					\item JONES, R. A., AND J. M. OSTROY (1984): ``Flexibility and Uncertainty,'' Review of Economic Studies, 51 (1), 13-32
					\item KOOPMANS, T. C. (1964): ``On the Flexibility of Future Preferences,'' in Human Judgments and Optimality, ed. by M. W. Shelly and G. L. Bryan. New York: Wiley.
					\item KREPS, D. M., AND E. L. PORTEUS (1978): ``Temporal Resolution of Uncertainty and Dynamic Choice Theory,'' Econometrica, 46 (1), 185-200.
\section{Take out repeats}
	Especially of references to BS2005: In some parts the paper also seem repeating itself: you review Bagwell and Staiger (2005) in Section 2.2 but you provide another summary of the same paper in Section 3. Again, a revised structure may reduce the overlap, make the paper shorter, and be more to the point.

\section{Make a bigger deal of the idea of $\ga$ decreasing function of $\tau$---move out of footnote}
\section{Big picture of which changes do what}
		\begin{tabular}{|l|c|c|}
			 & rigid & escape \\
			BS2005  & on-schedule (truthtelling): trivial; & need cost  \\
			 & off (repeated): optimal static if patient enough & \\
			$\ga(e)$ & on: trivial& no need, but revisit side payments\\
			 & off: mabye not b/c of lobby & \\
			$\ga(e,s)$ & ignore for now & is $s$ verifiable? def not w/$\ga(s,e)$
		\end{tabular}
